Capstone Movielens Report

### 2025-02-02 reports/capstone-movielens-report.Rmd
Citing using `citr` add-ins in R Studio.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
    - \hypersetup{backref,
          pdfpagemode=FullScreen,
          colorlinks=true,
          implicit=false}
    #- \hyper@nopatch@bib = null
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:

@@

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).

@@

This is a great conclusion, isn't is?!!

**References**

```{r results = "asis", echo = FALSE}
# \addcontentsline{toc}{section}{References} 
#\printbibliography[title={Whole bibliography}]
# 
# \color{black}
# \bibliography{references}
# \bibliographystyle{mla-good}
#\bibliographystyle{mla-good}
#\bibliographystyle{is-unsrt}
#\bibliographystyle{is-plain}
#\bibliographystyle{is-abbrv}
#\bibliographystyle{apalike}

PrintBibliography(bibFound,
                  .opts = list(check.entries = FALSE,
                               hyperlink = "to.bib",
                               first.inits = FALSE,
                               bib.style = "numeric",
                               style = "markdown",
                               cite.style = 'numeric'))

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
    - \usepackage[ natbib=true, style=numeric,sorting=none]{biblatex}
    - \hypersetup{backref,
          pdfpagemode=FullScreen,
          colorlinks=true,
          implicit=false}
    #- \hyper@nopatch@bib = null
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:

@@

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).

@@

This is a great conclusion, isn't it?!!
